On the Bit Complexity of Finding Points in Connected Components of a Smooth Real Hypersurface

### 2020-02-03 main.tex
Updated Section 9

$V \cap \pi_d^{-1}(\xb)$ has dimension zero. For $i\in\{1,\hdots,n\}$, we say that $f$ satisfies $\textbf{H}_i^{'}$ if 

@@

\item $\langle X_1,\hdots,X_i, f,  \frac{\pa f}{\pa X_{i+1}},\hdots,\frac{\pa f}{\pa X_n}\rangle $ is radical; 
\item $V(X_1,\hdots,X_i, f,  \frac{\pa f}{\pa X_{i+1}},\hdots,\frac{\pa f}{\pa X_n})$ has dimension $0$;
\item $V(X_1,\hdots,X_i, f,  \frac{\pa f}{\pa X_{i+1}},\hdots,\frac{\pa f}{\pa X_n})$ is smooth;

@@

Suppose that $f \in \Q[X_1,\hdots,X_n]$ satisfies \textbf{H}. Then there exists a Zariski closed set $\D \subset \mathbb{C}^{n^2}$ of degree at most $D^{\textrm{?}}$ such that, if $\textbf{A}$ is chosen from  $\C^{n^2}-\Delta$ ( $\Q^{n^2}-\Delta$?) then $f^A$ satisfies $\textbf{H}_i^{'}$ for all $i \in \{1,\hdots,n\}.$

@@

Fix $S \subset \mathbb{Q}$ with $|S| \geq \epsilon^{-1} D^{\textrm{?}}$ and $\epsilon > 0$. Then for $A\in S^{n^2}$ chosen randomly, the probability that $f^A$ satisfies $H_i^{'}$ for all $i \in \{1,\hdots,n\}$ is at least $1-\epsilon.$

@@

\section{Proof of Theorem 3.1}

@@

Assume that $f\in \Q[X_1,\hdots,X_n]$ satisfies $\textbf{H}.$

>>>>

$V \cap \pi_d^{-1}(\xb)$ has dimension zero. For $i\in\{1,\hdots,n\}$, and for a randomly chosen point $p_{i-1} = (x_1,\hdots,x_{i-1}) \in \Q^{i-1}$, we say that $f$ satisfies $\textbf{H}_i^{'}$ if 

@@

\item $\langle X_1-x_1,\hdots,X_{i-1}-x_{i-1}, f,  \frac{\pa f}{\pa X_{i+1}},\hdots,\frac{\pa f}{\pa X_n}\rangle $ is radical; 
\item $V(X_1-x_1,\hdots,X_{i-1}-x_{i-1}, f,  \frac{\pa f}{\pa X_{i+1}},\hdots,\frac{\pa f}{\pa X_n})$ is finite;
\item $V(X_1-x_1,\hdots,X_{i-1}-x_{i-1}, f,  \frac{\pa f}{\pa X_{i+1}},\hdots,\frac{\pa f}{\pa X_n})$ is smooth;

@@

Suppose that $f \in \Q[X_1,\hdots,X_n]$ satisfies \textbf{H}. Then there exists a Zariski closed set $\D \subset \mathbb{C}^{n^2}$ of degree at most $D^{\textrm{\td}}$ such that, if $\textbf{A}$ is chosen from  $\C^{n^2}-\Delta$ ( $\Q^{n^2}-\Delta$?) then $f^A$ satisfies $\textbf{H}_i^{'}$ for all $i \in \{1,\hdots,n\}.$

@@

Fix $S \subset \mathbb{Q}$ with $|S| \geq \epsilon^{-1} D^{\textrm{\td}}$ and $\epsilon > 0$. Then for $A\in S^{n^2}$ chosen randomly, the probability that $f^A$ satisfies $H_i^{'}$ for all $i \in \{1,\hdots,n\}$ is at least $1-\epsilon.$

@@

\section{Proof of Theorem 4.1}

@@

Recall Theorem 4.1: \textit{Suppose that $f \in \Q[X_1,\hdots,X_n]$ satisfies \textbf{H}. Then there exists a Zariski closed set $\D \subset \mathbb{C}^{n^2}$ of degree at most $D^{\textrm{\td}}$ such that, if $\textbf{A}$ is chosen from  $\C^{n^2}-\Delta$ ( $\Q^{n^2}-\Delta$?) then $f^A$ satisfies $\textbf{H}_i^{'}$ for all $i \in \{1,\hdots,n\}.$} 
Assume that $f\in \Q[X_1,\hdots,X_n]$ has degree at most $D$ and satisfies $\textbf{H}.$ By Theorem 6.1, there exists a zariski closed set $\D_1\subset \C^{n^2}$ with the property that, if $A \in \C^{n^2}-\D_1$ then, for $i \in \{1,\hdots,n\},$ $f^A$ satisfies $\textbf{H}_i^{'}(1), \textbf{H}_i^{'}(2),$ and $\textbf{H}_i^{'}(3).$ Likewise, by Theorem 7.1, we obtain $\D_2 \subset \C^{n^2}$ with the property that if $A \in \C^{n^2}-\D_2$ then $f^A$ satisfies $\textbf{H}_i^{'}(4), \textbf{H}_i^{'}(5),$ and $\textbf{H}_i^{'}(6).$ By Theorem 7.1, $\D_3 \subset \C^{n^2}$ exists with $f^A$ satisfying $\textbf{H}_i^{'}(7)$ when $A \in \C^{n^2}-\D_3$. Clearly then, if 
A \in \C^{n^2} - \bigcup_{i=1}^3 \D_i
then $f^A$ satisfies  $\textbf{H}_i^{'}$ for all $i \in \{1,\hdots,n\}.$ Take 
\Delta = \prod_{i=1}^3 \D_i,
and note that 
\deg \D \leq  \prod_{i=1}^3 \deg \D_i.
Recall Corollary 4.2: \textit{Fix $S \subset \mathbb{Q}$ with $|S| \geq \epsilon^{-1} D^{\textrm{\td}}$ and $\epsilon > 0$. Then for $A\in S^{n^2}$ chosen randomly, the probability that $f^A$ satisfies $H_i^{'}$ for all $i \in \{1,\hdots,n\}$ is at least $1-\epsilon.$}
Pr[A \in \Delta] \leq \frac{\deg \Delta}{|S|} \leq \frac{D^{\td}}{\epsilon^{-1}D^{\td}} = \epsilon.
